### 2022-09-29 main/frontmatter.tex
minor text tweaks; some abstract work

Nothing new appears, and supports the Standard Model in its continuing
successful extrapolation to the describe the most extreme behaviours colliding
protons.
Supersymmetry as a concept as not falsified by these results,
nor by the many similar observations.
But it is not confirmed.

Data are best interpreted if their theoretical and experimental background is
understood, so this thesis begins by introducing the theoretical and
experimental background to its search,
and the subtleties of its data-analysis procedures in their historical context.
\end{abstract}

>>>>

Nothing new appears, and supports the Standard Model in its continuing
successful extrapolation to the describe the most extreme behaviours colliding
protons.
Supersymmetry as a concept as not falsified by these results,
nor by the many similar observations.
But it is also not confirmed.

Data are best interpreted with an understanding of their background, so we
begin by introducing the theoretical and experimental background to our search,
and the subtleties of its data-analysis procedures in their historical context.
\end{abstract}
